\documentclass[xcolor=x11names,table]{article}

\usepackage{myDefaultPackageSetup/ArtRepBook/myDefaultsArtRepBook}

\title{(n)vim My Configurations}
\author{Mike Mengjie Huang}

\begin{document}
\maketitle
\tableofcontents

\section{What this document will cover}%
\label{sec:What this document will cover}
This document is supposed to cover some additional features, shortcuts and plugins
that I implemented. This is supposed to document some very important 
self-made and ``vim-made'' features that I don't want to forget about. Additionally
I will document some vim related things such as how includings in tex are used 
(and more).
\section{Additional Features}%
\label{sec:Additional Features}
\begin{multicols}{2}
\subsection{Navigation in Vim}%
\label{sub:Navigation in Vim}
\begin{itemize}
    \item Searching for file in subdirectory: \verb!<Ctl>p! and then search \item Browsing files with ranger: \verb!<Ctrl>n!
    \item Searching with NerdTree: \verb!<Space>n!
\end{itemize}
\subsection{Buffers}%
\label{sub:Buffers}
\begin{itemize}
    \item Look at buffers: \verb!:buffers! or \verb!<Ctrl>b!
    \item Opening buffer vertical: \verb!:vert sb<idx>!
    \item Opening buffer horizontally: \verb!sb<idx>!
    \item Delete buffer: \verb!<Space><Enter>!
\end{itemize}
\end{multicols}
\vspace{-5ex}
\subsection{Tabs and Tab-Navigation}%
\label{sub:Tabs and Tab-Navigation}
\vspace{-2ex}
\begin{multicols}{2}
\begin{itemize}
    \item Open tab: Use \verb!:tabedit! or \verb!<Space>t!
    \item Previous tab: \verb!gT! or \verb!<Space>,!
    \item Next tab: \verb!gt! or \verb!<Space>.!
    \item Go to a numbered tab: \verb!<idx>gt!
\end{itemize}
\end{multicols}
\end{document}
